ScPy: A SuperCollider Extension for Performing Numerical Computation via Embedded Python

### 2016-08-23 doc/paper.tex
use minted for code in the paper and other small improvements

\usepackage{fancyhdr} \usepackage{hyperref} \usepackage{listings}

@@

@@

Use of ScPy is through two UGens: \texttt{Py} and \texttt{PyOnce}. Both have one required argument,
a block of Python code. A map of variable names may optionally be provided to bind SuperCollider
variables to Python variables.  Additionally, there is a \texttt{DoneAction} argument which
specifies an action to occur in SuperCollider after the Python code has finished executing.

@@

\lstset{ caption={SuperCollider boilerplate for no-op FFT effect with ScPy.} }
\lstinputlisting[ basicstyle=\footnotesize\ttfamily]{../examples/template.sc}

@@

\section{Evaluation}

>>>>

\usepackage{fancyhdr} \usepackage{hyperref} \usepackage{listings} \usepackage{minted}

@@

\section{Usage}

Use of ScPy is through two UGens: \texttt{Py} and \texttt{PyOnce}. Both have one required argument,
a block of Python code. A map of variable names may optionally be provided to bind SuperCollider
variables to Python variables.  Additionally, there is an optional \texttt{DoneAction} argument which
specifies an action to occur in SuperCollider after the Python code has finished executing.

\begin{listing}[H] \inputminted[linenos=true]{SuperCollider}{../examples/template.sc}
\caption{SuperCollider boilerplate for no-op FFT effect with ScPy.} \label{lst:boilerplate}
\end{listing}

When listing \ref{lst:boilerplate} is run, an anonymous synth is created which will take in audio
from an external source, perform a STFT, process the spectral data with ScPy, perform an inverse
STFT, then finally output the resulting audio. Lines 8-9 contain Python code defining the
processing function where operations are to be inserted. Further examples will replace only those
lines.

@@

@@

@@
